Evolution of the AGN UV luminosity function

### 2017-06-12 Paper/paper.tex
Update plots

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic.pdf}
  \end{center}
  \caption{Luminosity function for $z=0.3$ to $2.6$.}
  \label{fig:mosaic}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic2.pdf}
  \end{center}
  \caption{Luminosity function for $z=2.6$ to $6.5$.}
  \label{fig:mosaic2}
\end{figure*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.6\textwidth,keepaspectratio]{emissivity.pdf}
  \end{center}
  \caption{LyC emissivity.}
  \label{fig:gammapi}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{evolution_global.pdf}
  \end{center}
  \caption{One possible global fit with a 12-parameter model.  Each
    double power law parameter has a 4th-order Chebyshev polynomial
    form.  Black points show result from Manti et al.~2017.}
  \label{fig:global_fit}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso.pdf}
  \end{center}
  \caption{Shouldn't there be cosmic downsizing?}
  \label{fig:rhoqso}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
  \end{center}
  \caption{Same as Figure~\ref{fig:rhoqso} but now with the global model.  This global model is the same as that shown in Figure~\ref{fig:global_fit}.}
  \label{fig:rhoqso_withGlobal}
\end{figure*}

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[width=\textwidth,keepaspectratio]{triangle.png}
%%   \end{center}
%%   \caption{Posteriors corresponding to Figure~\ref{fig:global_fit}.}
%%   \label{fig:triangle}
%% \end{figure*}

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[height=\textheight]{chains.pdf}
%%   \end{center}
%%   \caption{MCMC chains corresponding to Figure~\ref{fig:global_fit}.}
%%   \label{fig:chains}
%% \end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{evolution_cleaned.pdf}
  \end{center}
  \caption{Parameter evolution after making two changes to the
    analysis: (1) use \emph{only} BOSS quasars for $z=2.2$--$3.5$, and
    (2) use only $p>0.9$ quasars in the $z>3.7$ sample of Richards.
    The individual fits with these changes are shown in Figures
    \ref{fig:mosaic} and \ref{fig:mosaic2}.}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{evolution_model1.pdf}
  \end{center}
  \caption{My current global fit.  I am trying to understand why it is
    so bad.  See Figures~17--21 for more on this.  Note that now I am
    only trying to fit quasars with $z=0.6$--$2.2$ and $2.8$--$5.5$.
    I am trying to fit straight lines for $M_*$ and $\alpha$ and
    quadratics for $\phi_*$ and $\beta$.}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_model1.pdf}
  \end{center}
  \caption{The global fit is quite good at $z\sim 1$--$2$.}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth,keepaspectratio]{mosaic2_model1.pdf}
  \end{center}
  \caption{Previous figure continued.}
\end{figure*}

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[height=\textheight,keepaspectratio]{chains_model1.pdf}
%%   \end{center}
%%   \caption{MCMC chains for the global model of Figures~16--18.}
%% \end{figure*}

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[width=\textwidth,keepaspectratio]{triangle_model1.png}
%%   \end{center}
%%   \caption{Posteriors for the global model of Figures~16--18.}
%% \end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso_model1.pdf}
  \end{center}
  \caption{Quasar number density in the global model of Figure~16.}
\end{figure*}

>>>>

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic.pdf}
  \end{center}
  \caption{Individual luminosity function fits for $z=0.3$ to $2.6$.}
  \label{fig:mosaic}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic2.pdf}
  \end{center}
  \caption{Individual luminosity function fits for $z=2.6$ to $6.5$.}
  \label{fig:mosaic2}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso_allz.pdf}
  \end{center}
  \caption{AGN number density evolution, showing the systematic offset in BOSS quasars.}
  \label{fig:rhoqso_allz}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{evolution_alldata.pdf}
  \end{center}
  \caption{Parameter evolution from individual fits in
    Figures~\ref{fig:mosaic} and \ref{fig:mosaic2}.  Parameters from
    BOSS quasars are seen to be systematically offset. \textbf{[Show
        $z < 0.6$ point also?]}}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso.pdf}
  \end{center}
  \caption{AGN number density evolution with some BOSS quasars
    removed.}
  \label{fig:rhoqso}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{evolution_seldata.pdf}
  \end{center}
  \caption{Parameter evolution with some BOSS quasars removed.  We (1)
    use \emph{only} BOSS quasars for $z=2.2$--$3.5$, and (2) use only
    $p>0.9$ quasars in the $z>3.7$ sample of Richards.}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_withGlobal.pdf}
  \end{center}
  \caption{Individual and composite luminosity function fits for
    $z=0.3$ to $2.6$.  They do not agree for $2.2 < z < 2.6$ because
    composite fit does not consider quasars at those redshifts.}
  \label{fig:mosaic_withGlobal}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic2_withGlobal.pdf}
  \end{center}
  \caption{Individual and composite luminosity function fits for
    $z=2.6$ to $6.5$.  They do not agree for $2.6 < z < 2.8$ because
    composite fit does not consider quasars at those redshifts.}
  \label{fig:mosaic2_withGlobal}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{evolution_global.pdf}
  \end{center}
  \caption{Luminosity function parameter evolution in the global model.}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
  \end{center}
  \caption{AGN number density evolution in the global model.}
  \label{fig:rhoqso}
\end{figure*}

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{emissivity_18.pdf}
    \includegraphics[width=0.5\textwidth]{emissivity_20.pdf}
    \end{tabular}
  \end{center}
  \caption{LyC emissivity of AGN assuming 100\% escape fraction.
    Model luminosity functions are integrated down to $M_{1450}=-18$
    in the left panel and $-20$ in the right panel.}
  \label{fig:gammapi}
\end{figure*}

@@
